---
title: "HW2A Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library("learnr")
install.packages("testthat")
install.packages("remotes")
remotes::install_github("rstudio/gradethis")
#library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
gradethis::gradethis_setup()
```


## R Help

### Exercise 1

To use R help, type `help()`, with the name of the function you want help for inside of the parentheses. For example, to use R help to use the `data()` function, type and run the following:

```{r help_data, exercise=TRUE}
help(data)
```

## Loading datasets

### Exercise 1

To use data, you must first make it available in your environment. One way to do this is to read it in, as from an excel file. You'll do that in the HW, but it's not as useful to use on these online exercises.

To load data here, you can use the `data()` command, which will load a dataset that is already available in R. After skimming the help page for `data()`, run the command that will show you the list of all datasets available to load.

```{r available_datasets, exercise=TRUE, exercise.lines = 5}


```

```{r available_datasets-check}
grade_result(
  pass_if(~identical(.result, data()))
)
```

Then load the dataset that has data for an ELISA assay of DNAse.

```{r loading_datasets, exercise=TRUE}

```

```{r loading_datasets-solution}
data(DNase)
```

```{r loading_datasets-code-check}
grade_code()
```

Show that you properly loaded the data by showing the structure of the DNase dataframe.
Consult the `Base R` cheatsheet to find the function you need. 

```{r proper_loading, exercise=TRUE}


```

```{r proper_loading-check}
grade_result(
  pass_if(~identical(.result, str(DNase)))
)
```

## Installing R Packages

### Exercise 1

You can add new functions to R by installing new packages. Packages have a set of functions in that that can all be loaded into your R environment after installing. Let's install the package `seqinr`, a package that allows you to read in and work with DNA sequences. Consult the `Base R` cheatsheet to find the function you need, and run it below.

Inside of the function you should type 'seqinr'

*This package may take 1-2 minutes to install*

```{r installing_packages, exercise=TRUE}

```

```{r installing_packages-solution}
install.packages('seqinr')
```

```{r installing_packages-code-check}
grade_code()
```
## Loading R Packages

### Exercise 1

Now that the package is installed you can access its functions in one of two ways. Consult the `Base R` cheatsheet under *Using Packages* to find out how to do this.

First, you can call an individual function behind the name of the package. We'll do this for two functions below that will read in a sequence as DNA letters and then translate those leters into amino acids.

```{r loading_packages, exercise=TRUE}
toycds <- seqinr::s2c("tctgagcaaataaatcgg")
seqinr::translate(seq = toycds)
```

Another way to do this is to load all of the package's functions into your environment and call the functions without `seqinr::` in front of them. Find the function you need in the `Base R` cheatsheet and call it.

```{r library_packages, exercise=TRUE}

```

```{r library_packages-solution}
library('seqinr')
```

```{r library_packages-code-check}
grade_code()
```

Now call these commands. They should give the same answers as when you called them above.

```{r library_packages2, exercise=TRUE}
toycds2 <- s2c("tctgagcaaataaatcgg")
translate(seq = toycds2)
```

Convention is to library the package and then just call the function. But sometimes you need to call it specifically using the :: trick, especially if two packages have the same function name!

## Basic arithmetic

### Exercise 1

Let's review some basic arithmetic commands (help is available under the name `Arithmetic`). Review the documentation to understand how to

-add
-subtract
-multiply
-divide
-do integer division (i.e. `16/9 = 1`)
-get the remainder after dividing (i.e. `16/9 = 1`, remainder `7` (the function returns only `7`))
These are important arithmetic functions you'll use throughout your time with R.

First, add 21 and 3

```{r adding, exercise=TRUE}

```

```{r adding-check}
grade_result(
  pass_if(~identical(.result, 24))
)
```

Subtract 3 from 21

```{r subtracting, exercise=TRUE}

```

```{r subtracting-check}
grade_result(
  pass_if(~identical(.result, 18))
)
```

Multiply 21 by 3

```{r multiplying, exercise=TRUE}

```

```{r multiplying-check}
grade_result(
  pass_if(~identical(.result, 63))
)
```

Divide 21 by 9

```{r dividing, exercise=TRUE}

```

```{r dividing-check}
grade_result(
  pass_if(~identical(.result, (21/9)))
)
```

Perform integer division: divide 21 by 9

```{r integer_division, exercise=TRUE}

```

```{r integer_division-check}
grade_result(
  pass_if(~identical(.result, (21 %/% 9)))
)
```

Describe what integer devision is. Type your answer inside of print("YOUR ANSWER HERE")

```{r int_div_explanation, exercise=TRUE}

```

```{r int_div_explanation-solution}
print("Something similar to: Integer division is division where the remainder is discarded. For example, 21/9 = 2 and 3/9, but the 3/9 is removed so the answer is only 2.")
```


## Using variables

### Exercise 1

Complete the following exercises to show you can use variables.

Store the value `21` in the variable `var1`

```{r storing, exercise=TRUE}

```

```{r storing-solution}
var1 <- 21
```

```{r storing-code-check}
grade_code()
```

Store the value `3` in the variable `var2`

```{r storing2, exercise=TRUE}

```

```{r storing2-solution}
var2 <- 3
```

```{r storing2-code-check}
grade_code()
```

Calculate the product of `var1` and `var2`

```{r var_product, exercise=TRUE}

```

```{r var_product-check}
grade_result(
  pass_if(~identical(.result, 63))
)
```

Store the calculation of the product of `var1` and `var2` in the variable `var3`

```{r storing_product, exercise=TRUE}

```

```{r storing_product-solution}
var3 <- var1 * var2
```

```{r storing_product-code-check}
grade_code()
```

Print the value of `var3`

```{r print_var, exercise=TRUE}

```

```{r print_var-check}
grade_result(
  pass_if(~identical(.result, 63))
)
```

Change the value of the `var1` variable to `7`

```{r change_value, exercise=TRUE}

```

```{r change_value-solution}
var1 <- 7
```

```{r change_value-code-check}
grade_code()
```

Paste and rerun the code from three steps above, where you created the variable `var3`. Then print `var3`.

```{r paste_rerun, exercise=TRUE}

```

```{r paste_rerun-check}
grade_result(
  pass_if(~identical(.result, 21))
)
```

Notice that the same equation `var3 <- var1 * var2` gave you a different answer depending on the value assigned to `var1`. Be careful, because if you don't know the values stored in your variables you can get wrong answers!